ms_figures

### 2023-04-20 ms_figures.Rmd
fig3c min max geom ribbon

fig3c <- fig3c_data %>%
  ggplot(aes(x = year, y = supply_percent, color = supply_source)) +
  geom_line() +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

ggplot() +
  geom_line(data = artis_ts, aes(x = year, y = live_weight_t, color = hs_version), linetype = "dashed", linewidth = 1) +
  geom_line(data = custom_ts, aes(x = year, y = live_weight_t, color = hs_version), linewidth = 0.5, linetype = "solid") +
  scale_color_manual(
    values = c("Custom ARTIS Time series" = "black", "HS96" = "#741A32", "HS02" = "#B34232", "HS07" = "#D38F35", "HS12" = "red", "HS17" = "#114F59")
  ) +
  labs(x = "Year", y = "Live Weight (tonnes)", color = "HS Version") +
  theme_bw() +
  theme(legend.position = "bottom")

>>>>

fig3c <- ggplot() +
  geom_ribbon(data = fig3c_data %>%
                filter(supply_source == "domestic"),
              aes(ymin = supply_min_percent, ymax = supply_max_percent, x = year), fill = "grey70") +
  geom_ribbon(data = fig3c_data %>%
                filter(supply_source == "foreign"),
              aes(ymin = supply_min_percent, ymax = supply_max_percent, x = year), fill = "grey70") +
  geom_line(data = fig3c_data, aes(x = year, y = supply_percent, color = supply_source)) +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

ggplot() +
  geom_line(data = artis_ts, aes(x = year, y = product_weight_t, color = hs_version), linetype = "dashed", linewidth = 1) +
  geom_line(data = custom_ts, aes(x = year, y = product_weight_t, color = hs_version), linewidth = 0.5, linetype = "solid") +
  scale_color_manual(
    values = c("Custom ARTIS Time series" = "black", "HS96" = "#741A32", "HS02" = "#B34232", "HS07" = "#D38F35", "HS12" = "red", "HS17" = "#114F59")
  ) +
  labs(x = "Year", y = "Live Weight (tonnes)", color = "HS Version") +
  theme_bw() +
  theme(legend.position = "bottom")
